Greenhouse gas emissions model - making scenarios

### 2022-05-10 Scenarios_report.Rmd
trying to get varslice_resample to work

>>>>

# Probability of an increase in milk yield being associated with an increase in GHG emission intensity

GHG_simulation_scenarios$y[,"emission_intensity"]<-GHG_simulation_scenarios$y$pc_on_farm/GHG_simulation_scenarios$y$pc_milk_yield

GHG_sim_scen_y<-GHG_simulation_scenarios$y

GHG_sim_scen_y<-GHG_sim_scen_y[which(!is.infinite(GHG_sim_scen_y$emission_intensity)),]

uncertainty::varkernelslicerange(in_var = GHG_sim_scen_y$pc_milk_yield,
                                 out_var = GHG_sim_scen_y$emission_intensity, 
                                 min_in_var = round(min(GHG_sim_scen_y$pc_milk_yield)),
                                 max_in_var = round(max(GHG_sim_scen_y$pc_milk_yield)), 
                                 xlab_vars = "Emission intensity (XX/L) given milk yield range")

  in_var<-GHG_sim_scen_y$pc_milk_yield
  out_var<-GHG_sim_scen_y$emission_intensity
baseline_milk_yield <- min(in_var)
sliceb <-
  varslice_resample(in_var, out_var, expectedin_var = baseline_milk_yield, n_runs = 100000)
more_milk <- baseline_milk_yield
results <- data.frame(milk_yield = more_milk, probability = 0.5)

# the following isn't working yet
# I suspect this is because of an error in the varslice_resample function (and also the varkernelslice functions).
# I suspect the problem is in   Relative_probability <- in_outkernel$z[, expectedin_var]
# There may not be an expectedin_var'th column - this should be the column that corresponds to the x value expectedin_var

while (more_milk < max(in_var))
{
  more_milk <- more_milk + 10
  slice_more_milk <-
    varslice_resample(in_var,
                      out_var,
                      expectedin_var = more_milk,
                      n_runs = 100000)
  results <-
    rbind(results, c(more_milk, sum(sliceb > slice_more_milk) / length(sliceb)))
}
